Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene

### 2019-01-14 paper/paper.tex
Add changes to intro by Shih

%%%%%%%%%%%%%%%%%%%%
%Main
%%%%%%%%%%%%%%%%%%%%
\begin{document}
\clearpage{}
\begin{abstract}
  {\normalsize
    Atomically thin porous graphene membranes are emerging as one of
    the most promising candidates for the next-generation membrane
    technology owing to the ultrahigh permeation. However, the
    transport selectivity relies on the precise control over pore size
    and shape, considerably limiting the scalability. Here, we study
    electrolyte permeation through a sheet of large-area, porous
    graphene membrane, with relatively large pore sizes of 20$\pm$10
    nanometers. Counterintuitively, we observe macroscopic salt
    rejection by applying electrostatically gating, which reduces the
    diffusive flux by up to one order of magnitude. We systematically
    investigate the effects of salt concentration and species,
    including developing a theory to model the electrolyte diffusion
    through a nanopore in a sheet of gated graphene. The interplay
    between graphene quantum capacitance and the electrical double
    layer is found to selectively modulate the anionic and cationic
    transport paths, creating voltage-dependent electrochemical
    barriers when the pore size is comparable to the Debye length. Our
    findings reveal a new degree of freedom regulating electrolyte
    permeation through porous two-dimensional materials.

    % Atomically thin porous graphene membranes are emerging
    % as one of the most promising candidates as next-generation
    % membrane technology owing to their unique transport physics and
    % high permeation. Among the current challenges of 2D membranes is
    % the understanding of fundamental ion transport as well as its
    % control towards applications in ion rectification, ionic
    % transistors or desalination.  Here we report the study of
    % tailoring the ion transport through atomically-thin porous
    % graphene with pore sizes of 20$\pm$10 nanometers, and a pore
    % density of 1.25$\pm$0.25$\times$10$^{10}$ cm$^{-2}$. By
    % electrostatically gating a sheet of porous graphene, we
    % demonstrate a considerable reduction of salt flux by up to 55\%
    % and 85\% using a gate voltage, based on our experiments and
    % theoretical predictions, respectively. We systematically
    % investigate the effects of salt concentration and species,
    % including the development of a theory to model the electrolyte
    % diffusion through a nanopore in a sheet of gated graphene. The
    % interplay between graphene quantum capacitance and electrical
    % double layer is identified to be the main mechanism responsible
    % for the observed salt flux reduction, when the pore size is
    % comparable to the Debye length. Our findings reveal a new degree
    % of freedom controlling the membrane potential and electrolyte
    % permeation through porous two-dimensional materials.
  }
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage{}
\linenumbers
\section{Introduction}
\label{sec:intro}
A central objective in the emerging field of nanofluidics is to
control transport phenomena at nanometer scale to enable and study
novel devices and systems. The reduction of characteristic dimensions
in nanofluidics gives rise to substantially different transport
properties in comparison to their bulk counterparts
\cite{Schoch_2008}. In nanopores, for example, the effect of
surface-mediated transport becomes dominant when the pore size is
comparable to the characteristic length of diffusion, enabling new
applications such as ionic diodes \cite{Karnik_2007}, field-effect
transistors \cite{Nam_2009}, desalination \cite{Heiranian_2015}, and
nanopore-based DNA sequencing \cite{Heerema_2016,Garaj_2013}. Porous,
atomically thin two-dimensional (2D) materials, such as graphene, are
emerging as ideal membrane materials due to their ultimate permeation
\cite{Suk_2010,Jiang_2009,Celebi_2014,Koenig_2012,Drahushuk_2012}. Early
research has suggested that using nanoporous graphene as a
desalination membrane enables excellent salt rejection by preventing
the passage of ions, maintaining a high water permeability
simultaneously.
\cite{Cohen_Tanugi_2012,Suk_2014,Cohen_Tanugi_2014,Cohen_Tanugi_2015,O_Hern_2014,O_Hern_2015,Surwade_2015,Walker_2017,Ghosh_2018}. Nevertheless,
the fabrication of subnanometer porous 2D membranes over a large area
with atomic precision remains technically challenging
\cite{Suk_2014,Rollings_2016,O_Hern_2012,Wang_2017}. Moreover, a small
portion of excessively large pores can significantly diminish salt
rejection.  Very recently, a number of reports have explored the
effect of surface charges on the selectivity of ion transport through
graphene nanopores, as a consequence of the electrostatic interactions
between solvated ions and the charged functional groups attached on
graphene, indicating that even large pores ($>$ 30nm) can be ion
selective \cite{Rollings_2016,Surwade_2014}. However, it remains
controversial if surface charges effectively allow controlled
salt-transport or -rejection, as the membrane charge and potential
cannot be precisely quantified and are sensitive to the surroundings
and chemical treatment \cite{Li_2008}. Therefore, there is a lack of
fundamental understanding of the interactions between the atomically
thin 2D membrane, its surface charge and the electrolyte
solution. Here, we study macroscopic salt rectification through a
sheet of large-area porous graphene using electrostatic gating,
thereby deepening the understanding of ion-graphene interaction and
shedding light on applications of nanoporous graphene for tailored ion
transport.

@@

Next, we carried out the same experiments using the PG-covered PCTE
membrane (PG-PCTE), without electrostatic gating. The measured
diffusive flux values, $\boldsymbol{J}_{\mathrm{PG0}}$ (green bars in
\Fig{} \ref{fig:2}b), remain at the same order of magnitude compared
with those of bare PCTE membrane, suggesting that the transport
resistance of PCTE $R_{\mathrm{PCTE}}$, is dominant over that of PG
without gating, $R_{\mathrm{G}}^{0}$. Using a simple circuit model, we
estimate the ratio $\delta$ between $R_{\mathrm{G}}^{0}$ and
$R_{\mathrm{PCTE}}$, such that
$\delta = R_{\mathrm{PCTE}}/R_{\mathrm{G}}^{0}$, to be $\sim$2.2,
which is in good agreement with the value derived from the
experimental data in \Fig{} \ref{fig:2}b (details see Supplementary
Section \ref{SI-sec:R-model}).
% \todo[inline]{Make sure that the
  % values used are correct.}

>>>>

%%%%%%%%%%%%%%%%%%%%
%Main
%%%%%%%%%%%%%%%%%%%%
\begin{document}
\clearpage{}
\begin{abstract}
  {\normalsize
    Atomically thin porous graphene membranes are emerging as one of
    the most promising candidates for the next-generation membrane
    technology owing to the ultrahigh permeation. However, the
    transport selectivity relies on the precise control over pore size
    and shape, considerably limiting the scalability. Here, we study
    electrolyte permeation through a sheet of large-area, porous
    graphene membrane, with relatively large pore sizes of 20$\pm$10
    nanometers. Counterintuitively, we observe macroscopic salt
    rejection by applying electrostatically gating, which reduces the
    diffusive flux by up to one order of magnitude. We systematically
    investigate the effects of salt concentration and species,
    including developing a theory to model the electrolyte diffusion
    through a nanopore in a sheet of gated graphene. The interplay
    between graphene quantum capacitance and the electrical double
    layer is found to selectively modulate the anionic and cationic
    transport paths, creating voltage-dependent electrochemical
    barriers when the pore size is comparable to the Debye length. Our
    findings reveal a new degree of freedom regulating electrolyte
    permeation through porous two-dimensional materials.   
    % Atomically thin porous graphene membranes are emerging
    % as one of the most promising candidates as next-generation
    % membrane technology owing to their unique transport physics and
    % high permeation. Among the current challenges of 2D membranes is
    % the understanding of fundamental ion transport as well as its
    % control towards applications in ion rectification, ionic
    % transistors or desalination.  Here we report the study of
    % tailoring the ion transport through atomically-thin porous
    % graphene with pore sizes of 20$\pm$10 nanometers, and a pore
    % density of 1.25$\pm$0.25$\times$10$^{10}$ cm$^{-2}$. By
    % electrostatically gating a sheet of porous graphene, we
    % demonstrate a considerable reduction of salt flux by up to 55\%
    % and 85\% using a gate voltage, based on our experiments and
    % theoretical predictions, respectively. We systematically
    % investigate the effects of salt concentration and species,
    % including the development of a theory to model the electrolyte
    % diffusion through a nanopore in a sheet of gated graphene. The
    % interplay between graphene quantum capacitance and electrical
    % double layer is identified to be the main mechanism responsible
    % for the observed salt flux reduction, when the pore size is
    % comparable to the Debye length. Our findings reveal a new degree
    % of freedom controlling the membrane potential and electrolyte
    % permeation through porous two-dimensional materials.
  }
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage{}
\linenumbers
\section{Introduction}
\label{sec:intro}
A central objective in the emerging field of nanofluidics is to
control transport phenomena at nanometer scale to explore new
technological opportunities. The reduction of characteristic
dimensions in nanofluidics gives rise to substantially different
transport properties in comparison to their bulk counterparts
\cite{Schoch_2008}. In nanopores, for example, the effect of
surface-mediated transport becomes dominant when the pore size is
comparable to the characteristic length of diffusion, enabling new
applications such as ionic diodes \cite{Karnik_2007}, field-effect
transistors \cite{Nam_2009}, desalination \cite{Heiranian_2015}, and
nanopore-based DNA sequencing \cite{Heerema_2016,Garaj_2013}. Porous,
atomically thin two-dimensional (2D) materials, such as graphene, are
emerging as ideal membrane materials due to their ultimate permeation
\cite{Suk_2010,Jiang_2009,Celebi_2014,Koenig_2012,Drahushuk_2012}. Early
research has suggested that using a sheet of nanoporous graphene can
act as a desalination membrane by having the pore sizes smaller than
the hydrated radii ($\sim$1 nm), thereby hindering ion passage without
compromising water permeability
\cite{Cohen_Tanugi_2012,Suk_2014,Cohen_Tanugi_2014,Cohen_Tanugi_2015,O_Hern_2014,O_Hern_2015,Surwade_2015,Walker_2017,Ghosh_2018}. Nevertheless,
in practice, the fabrication of subnanometer porous 2D membranes over
a large area with atomic precision remains technically challenging
\cite{Suk_2014,Rollings_2016,O_Hern_2012,Wang_2017}. Moreover, a small
portion of excessively large pores or tears can significantly diminish
salt rejection.  Very recently, a number of reports have explored the
effect of surface charges on the selectivity of ion transport through
graphene nanopores, as a consequence of the electrostatic interactions
between solvated ions and the charged functional groups attached on
graphene, indicating that even large pores ($>$ 30nm) can be ion
selective \cite{Rollings_2016,Surwade_2014}. However, it remains
controversial if the surface charges can result in a degree of salt
rejection, as the surface charge and potential cannot be precisely
quantified and are sensitive to the surroundings as well as the
history of chemical treatment \cite{Li_2008}. There remains a lack of
fundamental understanding of the interactions between the charged 2D
nanopores and the electrolyte solution. In this report, we investigate
electrolyte permeation through graphene nanopores that are
significantly larger than the hydrated radii. We construct the surface
potential by taking into account of the elementary electronic
properties of graphene and demonstrate that a high degree of salt
rejection can be achieved by electrostatic gating.

@@

Next, we carried out the same experiments using the PG-covered PCTE
membrane (PG-PCTE), without electrostatic gating. The measured
diffusive flux values, $\boldsymbol{J}_{\mathrm{PG0}}$ (green bars in
\Fig{} \ref{fig:2}b), remain at the same order of magnitude compared
with those of bare PCTE membrane, suggesting that the transport
resistance of PCTE $R_{\mathrm{PCTE}}$, is dominant over that of PG
without gating, $R_{\mathrm{G}}^{0}$. Using a simple circuit model, we
estimate the ratio $\delta$ between $R_{\mathrm{G}}^{0}$ and
$R_{\mathrm{PCTE}}$, i.e.,
$\delta = R_{\mathrm{PCTE}}/R_{\mathrm{G}}^{0}$, to be $\sim$2.2,
which is in good agreement with the value derived from the
experimental data in \Fig{} \ref{fig:2}b (details see Supplementary
Section \ref{SI-sec:R-model}).
% \todo[inline]{Make sure that the
  % values used are correct.}
